Errorless irrationality: removing error-driven components from the inverse base-rate effect paradigm

### 2023-01-18 docs/manuscript.tex
transitional commit before sending it off
correct sample size for experiment 2

We recruited 65 undergraduate students who completed the experiment for partial course credit.
Recruitment was done via the SONA recruitment system. \\

@@

After exclusion, 30 participants made it into our analysis.
The group-level mean probabilities are shown in Table \ref{tab:results-exp2}.
The results are a qualitative and ordinal match to Experiment 1.
Participants showed a clear common preference for stimuli A, $M = 0.78$, 95\% HDI $[0.71, 0.85]$, $\mathrm{BF}_{10} = 7.72 \times 10^{8}$.

@@

There are alternative theories of the IBRE that do not rely on prediction-error driven processes.
A version of the dissimilarity-similarity general context model \cite<DGCM, >{stewart2007dissimilarity} modified by \cite{o2018model} has been proposed as an explanation of the IBRE.
From the perspective of DGCM, the main processes behind the rare preference are a combination of attention and dissimilarity from exemplars (stored category representations).
$BC \to rare$ arises due to the combination of two factors: the high salience of $C$ relative to $B$ and the impact of the dissimilarity of $BC$ to the common category exemplar on the decision process.
Nonetheless, the model can accommodate these results only informally because it does not specify the mechanisms which encode information and produce the attentional values of each stimulus.
DGCM is a model of the test phase.
In that sense, the current experimental manipulations cannot be represented in the model.
This is the same challenge we encountered with process models - the specifications of these theories are unable to incorporate the changes to the experimental procedure.

>>>>

We recruited 122 undergraduate students who completed the experiment for partial course credit.
Recruitment was done via the SONA recruitment system. \\

@@

After exclusion, 59 participants made it into our analysis.
The group-level mean probabilities are shown in Table \ref{tab:results-exp2}.
The results are a qualitative and ordinal match to Experiment 1.
Participants showed a clear common preference for stimuli A, $M = 0.78$, 95\% HDI $[0.71, 0.85]$, $\mathrm{BF}_{10} = 7.72 \times 10^{8}$.

@@

\subsection{Alternative Theories without Prediction Error}

There are alternative theories of the IBRE that do not rely on processes that calculate prediction error.
A version of the dissimilarity-similarity general context model \cite<DGCM, >{stewart2007dissimilarity} modified by \cite{o2018model} has been proposed as an explanation of the IBRE.
From the perspective of DGCM, the main processes behind the rare preference are a combination of attention and dissimilarity from exemplars (stored category representations).
$BC \to rare$ arises due to the combination of two factors: the high salience of $C$ relative to $B$ and the impact of the dissimilarity of $BC$ to the common category exemplar on the decision process.
Nonetheless, the model can accommodate these results only informally because it does not specify the mechanisms which encode information and produce the attentional values of each stimulus.
DGCM is a model of the test phase.
In that sense, the current experimental manipulations cannot be represented in the model.
This is the same challenge we encountered with process models - the specifications of these theories are unable to incorporate the changes to the experimental procedure.
